Target Markdown

### 2023-07-11 _targets.Rmd
Redo analysis with new simulations

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB"))
source(here::here("R", "network_metrics.R"))
source(here::here("R", "string_replacements.R"))
source(here::here("R", "model_helpers.R"))
```

@@

@@

```{r, message = FALSE}
library(tidyverse)
library(magrittr)
library(cowplot)
library(here)
library(arrow)
library(piecewiseSEM)
library(semEff)
library(easystats)
library(glmmTMB)
library(biglm)
```

```{r}
tar_read(sim_rho)
```

>>>>

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"))
source(here::here("R", "network_metrics.R"))
source(here::here("R", "string_replacements.R"))
source(here::here("R", "stability_decomposition.R"))
source(here::here("R", "model_helpers.R"))
```

@@

# New simulation

```{targets raw_sim}
list(
  tar_target(var_param_sim, c("rep", "productivity", "S", "ct", "rho", "env_stoch", "Z")),
  tar_target(sim_files_out, list.files(here::here("res", "simCSZenrich3/simCSZenrich3"))),
  tar_target(sim_files_ts,
    list.files(here::here("res", "simCSZenrich3")) %>% #
      .[str_detect(., "_ts")]
    ),
  tar_target(sim_param,
    map_dfr(sim_files_out,
      function (x) {
        open_dataset(here::here("res", "simCSZenrich3/simCSZenrich3", x),
          format = "arrow") %>%
        collect() %>%
        select(all_of(var_param_sim))
      })
    ),
  # Because I had to remove one ts that failed...
  tar_target(sim_param_ts,
    map_dfr(str_remove(sim_files_ts, "_ts")[str_remove(sim_files_ts, "_ts") %in% sim_files_out],
      function (x) {
        open_dataset(here::here("res", "simCSZenrich3/simCSZenrich3", x),
          format = "arrow") %>%
        collect() %>%
        select(all_of(var_param_sim))
      })
  ),
  tar_target(sim_prep,
        open_dataset(here::here("res", "simCSZenrich3/simCSZenrich3", sim_files_out),
          format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        filter(!is.na(richness)) %>%
        mutate(across(c(int_strength, max_int),
            ~map2(.x, S,
              function(y, rich) {
                matrix(y, nrow = rich)
              }
            )
          )
          ) %>%
        # Get matrix of alive species
        mutate(max_int_alive  = map2(max_int, bm_sp,
            function(mat, bm) {
              mask <- bm > 10^-6
              mat[mask, mask, drop = FALSE]
            }
          )
        ) %>%
        select(-max_int),
        pattern = sim_files_out
      ),
  tar_target(sim_net,
    sim_prep %>%
      mutate(
        persistence = richness / S,
        async = 1 / sync,
        stab_pop = 1 / avg_cv_sp,
        ct_alive = map_dbl(max_int_alive,
          ~ifelse(sum(.x) == 0, 0,
            sum(.x > 0) / ((ncol(.x))^2))),
        max_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
          ),
        avg_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
          ),
        sd_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) <= 1, 0, sd(.x[.x > 0]))
          ),
        cv_max_int_alive = sd_max_int_alive / avg_max_int_alive,
        inv_sd_max_int_alive = 1 / sd_max_int_alive,
        gini_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, gini(.x[.x > 0]))),
        avg_omnivory = map_dbl(omnivory, mean),
        disconnected_prod = map_lgl(max_int_alive,
          ~any(colSums(.x) == 0 & rowSums(.x) == 0))
        ) %>%
    select(!where(is.list))
  ),
  tar_target(sim_ts2_null,
    open_dataset(here::here("res", "simCSZenrich3", sim_files_ts),
          format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        mutate(is_null = map_lgl(species, is.null)) %>%
        select(is_null),
        pattern = sim_files_ts
        ),
  tar_target(sim_ts2,
    open_dataset(here::here("res", "simCSZenrich3", sim_files_ts),
          format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        filter(!map_lgl(species, is.null)) %>%
        mutate(
          stoch_d = map2(species, stoch, function(bm, d_stoch) {
            .1 * bm * exp(d_stoch)
            }),
          species = map(species, ~matrix(.x, nrow = 100)),
          stoch = map(stoch, ~matrix(.x, nrow = 100)),
          stoch_d = map(stoch_d, ~matrix(.x, nrow = 100)),
          cpe = map_dbl(species, compensatory_effect),
          cpe_env = map_dbl(stoch_d, compensatory_effect),
          cpe_int = cpe / cpe_env,
          stab_com = map_dbl(species, community_stability),
          pop_stab = map_dbl(species, population_stability),
          bm_sp = map(species, ~colMeans(.x)),
          bm_total = map_dbl(bm_sp, ~sum(.x)),
          sd_sp = map(species, ~apply(.x, 2, sd)),
          sum_sd_sp = map_dbl(sd_sp, ~sum(.x)),
          async = map_dbl(species, asynchrony),
          sae = map(species, statistical_averaging_effect),
          sae_total = map_dbl(sae, ~.x["total"]),
          sae_even = map_dbl(sae, ~.x["even"]),
          evenness_sae = map_dbl(sae, ~.x["eveness"])
        ) %>%
        select(-species, -stoch_d, -stoch),
        pattern = sim_files_ts
  ),
  tar_target(sim_stab, cbind(sim_param[!sim_ts2_null$is_null,], sim_ts2) %>% as_tibble()),
  tar_target(sim, left_join(sim_net %>% select(-async, -stab_com), sim_stab, by = var_param_sim)),
  tar_target(sim_fw,
    sim %>%
      filter(
        max_tlvl > 1,
        sum_sd_sp != Inf,
        bm_total > 10^-5,
        !disconnected_prod
        )
   ),
   tar_target(sim_fw_df, as.data.frame(sim_fw))
  )
```

## Species bm, sd and tlvl

```{targets sim_sp, tar_simple = TRUE}
sim_stab %>%
  select(all_of(c(var_param_sim, "sd_sp", "bm_sp"))) %>%
  left_join(
    sim_prep %>%
      select(all_of(c(var_param_sim, "tlvl", "alive_species")))
  ) %>%
  mutate(
    sd_sp = map2(sd_sp, alive_species, ~.x[.y]),
    bm_sp = map2(bm_sp, alive_species, ~.x[.y]),
    cv_sp = map2(sd_sp, bm_sp, ~.x / .y),
    tlvl_bm_sd_sp = pmap(list(tlvl, bm_sp, sd_sp, cv_sp, alive_species),
      function(x, y, z, a, b) {
        rbind.data.frame(list(
        species = b,
            tlvl = x,
            bm_sp = y,
            sd_sp = z,
            cv_sp = a
        )
        )
      }),
    check = map_lgl(tlvl_bm_sd_sp, ~is.null(nrow(.x)))
  ) %>%
  filter(!check) %>%
  select(all_of(c(var_param_sim, "tlvl_bm_sd_sp"))) %>%
  unnest(c(tlvl_bm_sd_sp))
```

## SEM

```{targets sem-process}
list(
  tar_target(sem_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_df),
      richness = lm(richness ~ ct + S, sim_fw_df),
      #  max_tlvl = lm(max_tlvl ~ ct + S + Z + productivity, sim_fw_df),
      w_avg_tlvl = lm(w_avg_tlvl ~ richness + ct_alive + productivity, sim_fw_df),
      avg_omnivory = lm(avg_omnivory ~ w_avg_tlvl + ct_alive + richness + productivity, sim_fw_df),
      avg_int_strength = lm(avg_int_strength ~ w_avg_tlvl + ct_alive + richness + productivity, sim_fw_df),
      pop_stab = lm(pop_stab ~ Z + richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + env_stoch + productivity, sim_fw_df),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive, sim_fw_df),
      sae_even = lm(sae_even ~ richness, sim_fw_df),
      cpe_int = lm(cpe_int ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + productivity, sim_fw_df),
      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_df)
    )
    ),
  tar_target(sem, as.psem(sem_model_list)),
  tar_target(sem_coeff, {
    ti <- summary(sem)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti #%>%
      #filter(abs(Std.Estimate) > 0.1)# %>%
#  mutate(
#    Response = var_replacement()[Response],
#    Predictor = var_replacement()[Predictor]
#  ) %>%
    }),
  tar_target(tab_sem_coeff,
    sem_coeff %>%
      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
      collapse_rows(1, valign = "middle") %>%
      kable_styling()
    ),
  tar_target(sem_collinearity,
    map_dfr(setNames(sem_model_list, names(sem_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_rsquared,
    map_dfr(sem_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

# plot

```{targets p-stab}
list(
  tar_target(p_cpe_env_rho, sim_fw %>%
    ggplot(aes(x = as.factor(1 - rho), y = cpe_env)) +
    geom_hline(yintercept = 1, linetype = "dashed") +
    geom_hline(yintercept = .5, linetype = "dashed", color = "red") +
    geom_boxplot() +
    labs(x = "Response diversity", y = "Env. Compensatory effect") +
    theme_bw()),
  tar_target(p_stoch_pop_stab,
    sim_fw %>%
      ggplot(aes(x = as.factor(env_stoch), y = pop_stab)) +
      geom_boxplot() +
      labs(x = "Environmental stochasticity", y = "Population stability") +
      theme_bw()),
    tar_target(p_prod_bm,
      sim_fw %>%
        filter(bm_total > 10^-5) %>%
        ggplot(aes(x = as.factor(productivity), y = log(bm_total))) +
        geom_boxplot() +
        labs(x = "Productivity", y = "Total biomass") +
        theme_bw()
      ),
    tar_target(p_prod_pop_stab,
      sim_fw %>%
        ggplot(aes(x = as.factor(productivity), y = log(pop_stab))) +
        geom_boxplot() +
        labs(x = "Productivity", y = "Population stability") +
        theme_bw()
    ),
    tar_target(p_stab_comp_stress,
      plot_grid(
        p_cpe_env_rho,
        p_stoch_pop_stab,
        p_prod_bm,
        p_prod_pop_stab,
        labels = "auto"
      )

    )

)

```

## Stability-diversity relationship

```{targets p-stab-rich}
list(
  tar_target(p_stab_s_prod,
    sim_fw %>%
      filter(productivity %in% c(5, 30), rho == 0, env_stoch == .2) %>%
      ggplot(aes(x = richness, y = stab_com, color = as.factor(productivity))) +
      geom_point() +
      geom_smooth() +
      labs(x = "Species richness", y = "Community stability", color = "Productivity") +
      theme_bw()),
    tar_target(p_stab_s_env_stoch,
      sim_fw %>%
        filter(env_stoch %in% c(.2, .6), rho == 0, productivity == 5) %>%
        ggplot(aes(x = richness, y = stab_com, color = as.factor(env_stoch))) +
        geom_point() +
        geom_smooth() +
        labs(x = "Species richness", y = "Community stability", color = "Env. variability") +
        theme_bw()),
      tar_target(p_stab_s_resp_div,
        sim_fw %>%
          filter(rho %in% c(0, 1), productivity == 5, env_stoch == .2) %>%
          ggplot(aes(x = richness, y = stab_com, color = as.factor(1 - rho))) +
          geom_point() +
          geom_smooth() +
          labs(x = "Species richness", y = "Community stability", color = "Response diversity") +
          theme_bw()
      ),
      tar_target(p_stab_s_stress,
         plot_grid(
           p_stab_s_prod,
           p_stab_s_env_stoch,
           p_stab_s_resp_div,
           labels = "auto"
         )
      )
)
```

## Interaction strength effect

```{targets p_int_stab, tar_simple = TRUE}
sim_fw %>%
  filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
  pivot_longer(c(stab_com, async, sae_total, cpe,
      sae_even, evenness_sae,
      cpe_int, cpe_env, stab_pop
      ), names_to = "async_decomp", values_to = "values") %>%
  mutate(async_decomp = var_replacement()[async_decomp]) %>%
  ggplot(aes(x = avg_int_strength, y = values)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Avg feeding rate", y = "Asynchrony component") +
  facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
  theme_bw()
```

```{targets p_int_fw, tar_simple = TRUE}
sim_fw %>%
  filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
  pivot_longer(c(richness, ct_alive, max_tlvl, avg_omnivory, w_avg_tlvl
      ), names_to = "fw_str", values_to = "values") %>%
  mutate(fw_str = var_replacement()[fw_str]) %>%
  ggplot(aes(x = avg_int_strength, y = values)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Avg feeding rate", y = "Food-web structure") +
  facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
  theme_bw()
```

## Avg Omnivory

```{targets p-omn}
list(
  tar_target(p_omn_stab,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .2) %>%
      pivot_longer(c(stab_com, pop_stab, async
          ), names_to = "stab_comp", values_to = "values") %>%
      mutate(stab_comp = var_replacement()[stab_comp]) %>%
      ggplot(aes(x = avg_omnivory, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Avg omnivory", y = "Stability component") +
      facet_wrap(~stab_comp, ncol = 3, scales = "free_y") +
      theme_bw()),
  tar_target(p_omn_fw,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .2) %>%
      pivot_longer(c(richness, ct_alive, w_avg_tlvl, max_tlvl
          ), names_to = "fw_str", values_to = "values") %>%
      mutate(fw_str = var_replacement()[fw_str]) %>%
      ggplot(aes(x = avg_omnivory, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Avg. Omnivory", y = "Food-web structure") +
      facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
      theme_bw()
  )
)
```

```{targets p-ct-rich-stab}
list(
  tar_target(p_ct_stab,
    sim_fw %>%
      filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
      pivot_longer(c(stab_com, async, sae_total, cpe,
          sae_even, evenness_sae,
          cpe_int, cpe_env, stab_pop
          ), names_to = "async_decomp", values_to = "values") %>%
      mutate(async_decomp = var_replacement()[async_decomp]) %>%
      ggplot(aes(x = ct_alive, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Connectance", y = "Asynchrony component") +
      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
      theme_bw()
    ),
  tar_target(p_rich_stab,
    sim_fw %>%
      filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
      pivot_longer(c(stab_com, async, sae_total, cpe,
          sae_even, evenness_sae,
          cpe_int, cpe_env, stab_pop
          ), names_to = "async_decomp", values_to = "values") %>%
      mutate(async_decomp = var_replacement()[async_decomp]) %>%
      ggplot(aes(x = richness, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Species richness", y = "Asynchrony component") +
      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
      theme_bw()
    )
)
```

```{targets p_cor, tar_simple = TRUE}
cor_var <- cor(
  sim_fw %>%
    select(c(richness, ct_alive, Z, bm_total,
        avg_int_strength, avg_omnivory, max_tlvl,
        rho, env_stoch, productivity,
        stab_com, pop_stab, async, sae_total, sae_even,
        evenness_sae, cpe, cpe_int, cpe_env)) %>%
  na.omit() %>%
  rename(any_of(get_rev_vec_name_val(var_replacement()))),
    method = "spearman")
ggcorrplot(cor_var, type = "lower", lab = TRUE)
```

@@

```{r, message = FALSE}
library(tidyverse)
library(magrittr)
library(cowplot)
library(here)
library(arrow)
library(piecewiseSEM)
library(semEff)
library(easystats)
library(glmmTMB)
library(ggcorrplot)
source(here::here("R", "network_metrics.R"))
source(here::here("R", "string_replacements.R"))
source(here::here("R", "stability_decomposition.R"))
source(here::here("R", "model_helpers.R"))
```

```{r}
tar_load(sim_prep)
map(sim_prep$omega[1:5], length)
```

```{r}
tar_load(sim_fw)
colnames(sim_fw)
summary(sim_fw$avg_int_strength)
unique(sim_fw$Z)
tar_read(p_cor)
tar_read(p_prod_pop_stab)
tar_read(p_stab_s_stress)

sim_fw %>%
  filter(env_stoch == .2, rho %in% c(0, .4, 1), productivity == 5) %>%
  ggplot(aes(x = richness, y = cpe_env, color = as.factor(rho))) +
  geom_point() +
  labs(x = "Species richness", y = "Comp. effects (Environment)") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(productivity), y = pop_stab, color = as.factor(Z))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(productivity), y = stab_com, color = as.factor(Z))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(Z), y = pop_stab, color = as.factor(productivity))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(Z), y = avg_int_strength, color = as.factor(productivity))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0, bm_total > 10^-5) %>%
  ggplot(aes(x = as.factor(Z), y = bm_total, color = as.factor(productivity))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(Z), y = evenness_sae, color = as.factor(productivity))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(productivity), y = cpe_int, color = as.factor(Z))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()
```

```{r}
var_fw_struct <- c("richness", "ct_alive", "Z")
var_fw_emergent_struct <- c("max_tlvl", "w_avg_tlvl", "avg_omnivory")
var_fw_flux <- c("avg_int_strength")
var_stab <- c("async", "stab_com", "pop_stab")
```

```{r, eval = FALSE}
#colnames(simZ)
pairs(sim_fw %>%
  filter(env_stoch == .2) %>%
  select(c(var_fw_struct, var_fw_emergent_struct, var_fw_flux, stab_pop)))
```

```{r}
tar_load(sim_sp)

sim_sp %>%
  filter(env_stoch == .2, rho == 1, Z == 10) %>%
  ggplot(aes(x = tlvl, y = log(cv_sp))) +
  geom_point() +
  geom_smooth()
```

```{r}

tar_read(sem_coeff) %>%
  filter(abs(Std.Estimate) > .1)
tar_read(sem_rsquared)
tar_load(sem_collinearity)
sem_collinearity %>%
  print(., n = 38)
```

```{r}
tar_load(sem_model_list)
tar_load(sim_fw_df)
sem_boot <- bootEff(sem_model_list,
  R = 10, seed = 13, parallel = "no")

sem_eff <- semEff(sem_model_list, ci.type = "perc", R = 10, seed = 13, parallel = "no")
```

```{r}
mod_tot_scaled <- lm(stab_com ~
  richness + productivity + rho + env_stoch +
  ct_alive + avg_int_strength + avg_omnivory + w_avg_tlvl +
  richness : productivity +
  richness : rho +
  richness : env_stoch +
  richness : ct_alive +
  richness : avg_int_strength +
  richness : avg_omnivory +
  richness : w_avg_tlvl +
  richness : productivity : ct_alive +
  richness : productivity : w_avg_tlvl +
  richness : productivity : avg_int_strength +
  richness : productivity : avg_omnivory +
  richness : rho : ct_alive +
  richness : rho : w_avg_tlvl +
  richness : rho : avg_int_strength +
  richness : rho : avg_omnivory +
  richness : env_stoch : ct_alive +
  richness : env_stoch : w_avg_tlvl +
  richness : env_stoch : avg_int_strength +
  richness : env_stoch : avg_omnivory,
sim_fw %>%
  mutate(across(c("stab_com", "richness", "productivity", "rho", "env_stoch", "ct_alive", "avg_int_strength", "avg_omnivory", "w_avg_tlvl"), scale))

  )
summary(mod_tot)
predict(mod_tot)
summary(sim_fw$avg_int_strength)
summary(sim_fw$w_avg_tlvl)
summary(sim_fw$avg_omnivory)

mod_tot <- lm(stab_com ~
  richness + productivity + rho + env_stoch +
  ct_alive + avg_int_strength + avg_omnivory + w_avg_tlvl +
  richness * productivity +
  richness * rho +
  richness * env_stoch +
  richness * ct_alive +
  richness * avg_int_strength +
  richness * avg_omnivory +
  richness * w_avg_tlvl +
  richness * productivity * ct_alive +
  richness * productivity * w_avg_tlvl +
  richness * productivity * avg_int_strength +
  richness * productivity * avg_omnivory +
  richness * rho * ct_alive +
  richness * rho * w_avg_tlvl +
  richness * rho * avg_int_strength +
  richness * rho * avg_omnivory +
  richness * env_stoch * ct_alive +
  richness * env_stoch * w_avg_tlvl +
  richness * env_stoch * avg_int_strength +
  richness * env_stoch * avg_omnivory,
mutate(sim_fw, across(c(stab_com, richness), log)) #, richness
  )
check_collinearity(lm(stab_com ~ richness + productivity + rho + env_stoch +
  ct_alive + avg_int_strength + avg_omnivory + w_avg_tlvl, sim_fw))
plot(mod_tot)

pred_data <- list(
  richness = log(seq(5, 30, 1)),
  ct_alive = c(.05, .10, .30),
  rho = c(0, .5, 1),
  avg_int_strength = c(.02, .04, .1),
  env_stoch = c(.2, .6),
  w_avg_tlvl = c(1.5, 1.7, 2),
  avg_omnivory = c(.01, .05, .1),
  productivity = c(5, 30),
  Z = 10
  ) %>% expand.grid()
pred_data$stab_com <- predict(mod_tot, newdata = pred_data)

```

```{r}
pred_data %>%
  filter(
    productivity == 5,
    ct_alive %in% c(.1, .3),
    rho %in% c(0, 1),
    avg_int_strength %in% c(.02, .1),
    avg_omnivory == .05,
    w_avg_tlvl == 1.7) %>%
  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
  geom_line() +
  facet_grid(cols = vars(env_stoch), rows = vars(rho))

pred_data %>%
  filter(
    rho == 0,
    ct_alive %in% c(.1, .3),
    avg_int_strength %in% c(.02, .1),
    avg_omnivory == .05,
    w_avg_tlvl == 1.7) %>%
  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
  geom_line() +
  facet_grid(cols = vars(env_stoch), rows = vars(productivity), labeller = label_both)

pred_data %>%
  filter(
    env_stoch == 0.2,
    ct_alive %in% c(.1, .3),
    rho %in% c(0, 1),
    avg_int_strength %in% c(.02, .1),
    avg_omnivory == .05,
    w_avg_tlvl == 1.7) %>%
  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
  geom_line() +
  facet_grid(cols = vars(rho), rows = vars(productivity), labeller = label_both) +
  theme_bw() +
  labs(
    x = "Species richness",
    y = "Community stability",
    linewidth = "Avg. Int",
    color = "Connectance"
  )
```

```{r}
pred_data %>%
  filter(
    env_stoch == 0.6,
    ct_alive %in% c(.1, .3),
    rho %in% c(0, 1),
    avg_int_strength %in% c(.02, .1),
    avg_omnivory == .05,
    w_avg_tlvl == 1.7) %>%
  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
  geom_line() +
  facet_grid(cols = vars(rho), rows = vars(productivity)) +
  theme_bw()
```
